---
title: "Rain Precipitation and rainforest burn in Brazil"
author: "Luiz Bergo"
date: "20/02/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Recently Brazil suffered with a large number of rainforest burns, that shed light on environmental issues main of that regarding the use of rainforest spaces to accomodate cattle pasture.  

A common process of turn forests in pasture is by means of controlled fire. Environmentalist advise about the problem that pratice may cause to the overall environment, with attention to the most precious resource of the world, water.  

The data used in this study are gently offered by Kaggle team at:  

<https://www.kaggle.com/fabiopotsch/precipitation-in-brazil>   <https://www.kaggle.com/gustavomodelli/forest-fires-in-brazil>


### Rain vs. Rain forest burn

This graphic depict the total rain at some states where most of rainforest burn are detected.

### Annual rainfall precipitation
```{r rain_total, echo = FALSE}
library(plotly)
library(dplyr)

df_trb <- read.csv2("total_rain_burn.csv")

with(df_trb,
  plot_ly(x = ~year, y = ~sum_preciptation  , type = "scatter" ,  mode = "markers" , color = "blue") %>%
   layout(
    title = 'Rainfall at burn area from 1.998 to 2.017',
    xaxis = list(
      title = 'Year'
    ),
    yaxis = list(
      range = c(0, 50000),
      title = 'Annual Precipitation'
    )
  )
)


```


This graphic depict the total rainforest burn at some states with more occurence.


```{r burn_total, echo = FALSE}
library(plotly)
library(dplyr)

with(df_trb,
  plot_ly(x = ~year, y = ~sum_burn  , mode = "markers" , color = "red") %>%
   layout(
    title = 'Rainforest burn at burn area from 1.998 to 2.017',
    xaxis = list(
      title = 'Year'
    ),
    yaxis = list(
      range = c(0, 245000),
      title = 'Annual number of rainforest burn'
    )
  )
)


```

Both of data indicates a seasonal behavior, although is the past few years there is a clearly trend in both of them showing increasing in forest burn an decreasing in rainfall levels.  

One question that is commomly raised is if the absence of rain causes the rainforest burns, observing the picture below this is not clearly related, indicating the need to investigate in depth the contribution for this problem.



```{r burn_rain, echo = FALSE}
library(plotly)
library(dplyr)

with(df_trb,
  plot_ly(x = ~sum_preciptation, y = ~sum_burn  , mode = "markers" , color = "green") %>%
   layout(
    title = 'Precipitation vs. Rainforest burn from 1.998 to 2.017',
    xaxis = list(
      title = 'Rainfall'
    ),
    yaxis = list(
      range = c(0, 245000),
      title = 'Annual number of rainforest burn'
    )
  )
)


```

### Conclusion

This study is just to practice the use of R package *plotly* but for the sake of convenience the author attempt to bring some data that may lead other pratictioners to understand and contribute for something so important that is our Earth.

